---
title: "Exploratory Data Analysis"
author: "STOR 320.02 Group 2"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)

SALARY <- read_csv("salary_data.csv")
# Import Data Below
# read_csv()
```

# Creator: Casey Dulaney

### Q1: Which companies have the highest ratings?

```{r}
#
```

### Q2: What is the geographic distribution of the job locations?

```{r}
#
```

# Interpreter1: Weiye Zhang

### Q1: What is the relationship between the average salary and the rating of the company?

```{r}
#
```

### Q2:Which job location has the highest paying jobs on average?

```{r}
#
```

# Interpreter2: Serhat Çalıkoğlu

### Q1: What is the relationship between size and salary?

```{r}

ggplot(data = SALARY) +
        stat_summary(
          mapping = aes(x = Size, y = AvgSalary),
          fun.ymin = min,
          fun.ymax = max,
          fun.y = median
)


```

### Q2: What is the relationship between size and headquarter location?

```{r}
SALARY = rename(SALARY,JobLocation = 'Job Location')
```


```{r}
ggplot(data = SALARY)+
  geom_bar(aes(x =Size, fill = JobLocation))
```

# Orator1: Nathaniel McCraw

### Q1: What is the relationship between age of the company and the rating of the company?

```{r}
#
```

### Q2: Does a relationship between headquarter location and company rating exist?

```{r}
#
```


# Orator2: Ryan Kenney

### Q1: What company pays their employees the most?

```{r}
#
```

### Q2: What is the relationship between age of company and salary?

```{r}
#
```

# Deliverer: Aijia Zhang

### Q1: What is the relationship between type of industry and salary? (finance/healthcare...)

```{r}
#
```

### Q2: What is the relationship between type of ownership and salary? (private/ public/government...)

```{r}
#
```

# Follow-up Questions

### New Questions Based Off Initial Investigation

- Q1: WRITE_QUESTION_HERE
- Q2: WRITE_QUESTION_HERE
- Q3: WRITE_QUESTION_HERE 
- Q4: WRITE_QUESTION_HERE

### Investigation of Follow-up Questions

GIVE WHAT 2 QUESTIONS YOU ATTEMPTED TO INVESTIGATE FURTHER IN COMPLETE SENTENCES (*Example:* Our group decided to investigate Q2 and Q4 in further detail.)

SHOW AT LEAST 2 TABLES OR FIGURES BELOW THAT EXPLORE ANSWERS FOR THE QUESTIONS YOU ARE INVESTIGATING FURTHER.

```{r}
#
```

```{r}
#
```

# Summary

GIVE A 2 PARAGRAPH SUMMARY. 

PARAGRAPH 1 SHOULD DESCRIBE WHAT YOU LEARNED ABOUT YOUR DATA FROM INVESTIGATING THE INITIAL QUESTIONS. DID YOU FIND ANYTHING UNUSUAL IN YOUR DATA? DID ANYTHING SURPRISE YOU? WHICH OF THE INITIAL QUESTIONS WERE HELPFUL IN LEADING YOU TO MORE QUESTIONS?

PARAGRAPH 2 SHOULD SUMMARIZE WHAT YOU LEARNED FROM INVESTIGATING THE FOLLOW-UP QUESTIONS. WHY ARE THESE FOLLOW-UP QUESTIONS INTERESTING FOR INVESTIGATION? DESCRIBE THE TABLES/FIGURES YOU USED TO EXPLORE ANSWERS TO THESE FOLLOW-UP QUESTIONS? WHAT DID YOU LEARN FROM THE TABLES/FIGURES REGARDING THE FOLLOW-UP QUESTIONS YOU PROPOSED?















